Visual Search and Pre-crastination

### 2023-09-01 RegReport/paper.tex
Summary stats for key measures

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_prior_plot.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

The range of precrastination behaviours is shown in Figure (\ref{fig:exp2_strat_summary}(b). The majority of participants clearly either pre-crastinated (117, $58.5\%$) or not (71, $35.5\%$) with only a small minority (11, $5.5\%$) following an intermediate strategy. As such, we will treat pre-crastination as a two-level factor and exclude participants exhibiting intermediate behaviours.

@@

\begin{figure}[t]
  \centering  
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/prior_plot.pdf}}
  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:full_exp_strategy}
\end{figure}

>>>>

\begin{figure}[t]
  \centering  
  %\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_prior_plot.pdf}}
  %\subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/pilot_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:exp1_strategy}
\end{figure}

@@

The range of precrastination behaviours is shown in Figure (\ref{fig:exp2_strat_summary}(b). The majority of participants clearly either pre-crastinated (180, $59.0\%$) or not (105, $34.4\%$) with only a small minority (20, $6.5\%$) following an intermediate strategy. As such, we will treat pre-crastination as a two-level factor and exclude participants exhibiting intermediate behaviours.

@@

\begin{figure}[t]
  \centering  
 % \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/prior_plot.pdf}}
%  \subfigure[]{\includegraphics[width=6cm]{../analysis/scratch/post_plot.pdf}}
  \caption{(a) Prior and (b) posterior distributions for the mean of the two groups of participants, and the difference between them. Our priors for the two groups are identical, hence the overlapping distributions.}
  \label{fig:full_exp_strategy}
\end{figure}

### 2023-09-01 analysis/2_registered.Rmd
Summary stats for key measures

```{r}
dat_s <- read_csv("scratch/dat_rt_acc_strat.csv")
dat_p <- read_csv("scratch/prcrastination_and_personality.csv") %>%
  mutate(pre_crastinate = as_factor(pre_crastinate),
         pre_crastinate = fct_relevel(pre_crastinate, "yes", "intermediate", "no"))

@@

## Visual Search Accuracy and Response Time

@@

dat %>% ggplot(aes(targ_side_rel, accuracy, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
    scale_x_discrete("trial type")  +
  theme(legend.position = "none")  -> plt_acc

dat %>% ggplot(aes(targ_side_rel, median_rt, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
  theme(legend.justification=c(1,0), legend.position=c(1,0)) + 
  scale_x_discrete("trial type")  +
  scale_y_log10("reaction time (seconds)")  -> plt_rt

@@

@@

rm(plt_acc, plt_rt)
```

>>>>

```{r}
dat_s <- read_csv("scratch/dat_rt_acc_strat.csv")

dat_p <- read_csv("scratch/prcrastination_and_personality.csv") %>%
  filter(!is.na(pre_crastinate)) %>%
  mutate(pre_crastinate = as_factor(pre_crastinate),
         pre_crastinate = fct_relevel(pre_crastinate, "no", "intermediate", "yes"))

@@

## Visual Search Accuracy & Response Time

@@

dat %>% ggplot(aes(targ_side_rel, accuracy, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
    scale_x_discrete("trial type")  +
  theme(legend.justification=c(0,0), legend.position=c(0,0))  -> plt_acc

dat %>% ggplot(aes(targ_side_rel, median_rt, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
  theme(legend.position = "none") + 
  scale_x_discrete("trial type")  +
  scale_y_log10("reaction time (seconds)")  -> plt_rt

@@

```{r}
rm(plt_acc, plt_rt)
```

## Search Strategy & Pre-crastination

```{r}
dat_s %>% 
  group_by(person) %>%
  summarise(search_strat = unique(prop_hard)) -> dat_strat

dat_strat %>%
  ggplot(aes(search_strat)) + 
  geom_histogram(breaks = seq(0.0, 1, 0.1), colour = "black") + 
  scale_x_continuous("search strategy score") -> plt

ggsave("scratch/strat_hist.pdf", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 3)

And now look at pre-crastination measure.

@@

dat_p %>% ggplot(aes(x = n_pc)) +
  geom_histogram(bins = 7, alpha = 0.67, colour = "black") +
  scale_x_continuous("number of trials") + 
  scale_fill_viridis_d() +
  theme(legend.position = "none") -> plt1

dat_p %>% ggplot(aes(x = pre_crastinate)) + 
  geom_bar() +
  scale_x_discrete("pre-crastination classification") + 
  scale_fill_viridis_d() +
  theme(legend.position = "none") -> plt2

plt1 + plt2

ggsave("scratch/pre_crastinate.pdf", plt2 + theme_bw(),  width = 4, height = 3)

We have replicated the original pre-crastination finding....

```{r}
n_row <- nrow(dat_p)

dat_p %>% 
  group_by(pre_crastinate) %>%
  summarise(n = n(),
            percentage = 100*n/n_row) %>%
  knitr::kable()

rm(n_row)
```
